Predicting FOMC Actions using ML and NLP

### 2019-05-02 presentation/paper.tex
paper update

@@

\begin{figure}[h!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[height=2in,width=2in]{../text/data_for_graphs/accuracy.pdf}
\caption{Accuracy peaks at around 10 iterations}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[height=2in,width=2in]{../text/data_for_graphs/F1.pdf}
  \caption{A subfigure}
  \label{fig:sub2}
\end{subfigure}
\caption{F1 also peaks at around 10 iterations}
\label{fig:test}
\end{figure}

@@

\bibitem{stanford} Puri, Indira \emph{USING MACHINE LEARNING TO PREDICT INTEREST RATE CHANGES FROM FEDERAL RESERVE PROCEEDINGS}
\end{thebibliography}

>>>>

\begin{figure}[h!]
\begin{center}
\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/log_lass_accuracy_more iterations".pdf}
\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/log_reg_accuracy_more iterations".pdf}
\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/NB_accuracy_more iterations".pdf}
\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/SVM_accuracy_more iterations".pdf}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/log_lasso_f1".pdf}
\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/log_f1".pdf}
\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/naive_bayes_f1".pdf}
\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/SVM_f1".pdf}
\end{center}
\end{figure}

@@

\bibitem{stanford} Puri, Indira \emph{Using Machine Learning to Predict Interest Rate Changes from Federal Reserve Proceedings}
\end{thebibliography}
